---
title: "Week_6_HW"
author: Weizi Wu
format: pdf
editor: visual
---

## Week6_HW

1.  What purpose to Makefile serve?

    Data clean up, data gathering, or files merging

2.  What is the function to download a URL?

    import() or read.table if easily accessible

3.  What is a .zip file?

    Compressed files

4.  What is the process to download and decompress a .zip file? Give an example in a R code chunk.

    a\. Specify the URL of the .zip file and the destination folder

    b\. Create a temporary file called 'temp'

    c\. Download the compressed file into the temporary file

    d\. Decompress the file and convert it into a data frame

    e\. Delete the temporary file

```{r zip}
#specify the URL
URL <- paste0("http://www.unified-democracy-scores.org/", "files/20140312/z/uds_summary.csv.gz")
#create temporary file
temp <- tempfile()
download.file(URL, temp)
##Decompress the file
uds_data <- read.csv(gzfile(temp, "uds_summary.csv"))
##Delete the temp
unlink(temp)
```

5.  What are APIs?

    Application Programming Interfaces

6.  Use WDI package to download a new dataset other than AG.CON.FERT.ZS

    ```{r WDI, echo=FALSE}
    #Load WDI package
    library(WDI)
    # Search World Bank for fertilizer consumption data
    WDIsearch("fertilizer consumption")
    fert_cons_data <- WDI(indicator = "AG.CON.FERT.PT.ZS",
    start = 2012, end = 2022)
    head(fert_cons_data)
    ```

7.  Indicate 3 new things you learned from this week.

a. I learned to extract data from public website

b. I learned API and related package---WDI

c. I leanred to download zip files with URLs
